\documentclass[smallextended]{svjour3}
%\documentclass[10pt]{article}
\usepackage{xcolor,graphicx,import,fullpage,textcomp,colortbl,array,pgfplots,lscape,todonotes,booktabs,dsfont,marvosym,ulem} \usepackage[fleqn]{amsmath}% textgreek
\usepackage{graphicx,subcaption,caption,pgfplots,amsfonts}
	\newlength\figureheight
	\newlength\figurewidth
\definecolor{grey}{gray}{0.5}
\definecolor{lightgrey}{gray}{0.8}
\usepackage[sort,numbers]{natbib} %[numbers]
%\usepackage[papersize={85cm,30cm},left=2cm,top=2cm]{geometry}
%\usepackage[a3paper,left=2cm,top=4cm,bottom=4cm]{geometry}

\usepackage{nccmath}

\def\ns{\vspace{-.06truein}}
\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}
\usepackage{multirow}
%if you are annoyed of the colored boxes the hyperlinks in the pdf file uncomment this instead of the plain hyperref package above:
\usepackage[colorlinks=true, linkcolor=black, citecolor=black, urlcolor=black]{hyperref}
\usepackage{NVC} %calls the style package NVC.sty created by Loes and Evert
\usepackage{glossaries,textgreek,bm}
\usepackage{hyperref}
\usepackage[framed,numbered,autolinebreaks,useliterate]{mcode}
\usepackage[toc,page]{appendix}
\newglossary[slg]{symbolslist}{syi}{syg}{List of symbols} %Generate a list of symboles
\renewcommand*{\glspostdescription}{} %Remove the dot at the end of glossary descriptions
\makeglossaries %Activate glossary commands
\usepackage{glossaryEntries}
\usepackage{amsmath}
\usepackage{algorithm,algpseudocode}
\numberwithin{equation}{section}
\definecolor{darkred}{rgb}{.8,0,0}
\definecolor{darkgreen}{rgb}{0,.6,0}
\newcommand{\add}[1]{\textcolor{darkgreen}{\uline{#1}}}
\newcommand{\remove}[1]{\textcolor{darkred}{\sout{#1}}}
% \Add{} and \Del{} Corrections and \Mark{}
%\usepackage[active,new,noold,marker]{xrcs}
%%%%%%%%%%%%
\newcommand{\ca}{Ca$^{\text{\scriptsize 2+}}$}
\newcommand{\ip}{IP$_{\text{\scriptsize 3}}$ }
\newcommand{\jplc}{J$_{\text{\scriptsize PLC}_{\text{\scriptsize agonist}}}$}
\newcommand{\na}{Na$^{\text{\scriptsize +}}$}
\newcommand{\pot}{K$^{\text{\scriptsize +}}$}
\newcommand{\cl}{Cl$^{\text{\scriptsize -}}$}
\newcommand{\kca}{K$_{\text{\scriptsize Ca}}$}
\linespread{2.0}\include{./glossary}
\newcommand{\psec}{s$^{-1}$\xspace}
\begin{document}
\title{Analysing High-Dimensional Neuroscience Models: Neurovascular Coupling. }
\author{ T. David \and P.A. Gremaud  \thanks{P.A.G. was supported in part by National Science Foundation (NSF) awards NSF DMS-1522765 and DMS-1745654.}\and J.L. Hart\thanks{J.L.H. was supported in part by the National Science Foundation (NSF) award NSF DMS-1522765.}}
\institute{T. David \at Department of Mechanical Engineering, University of Canterbury, New Zealand, \email{tim.david@canterbury.ac.nz} \and P.A. Gremaud \at Department of Mathematics, North Carolina State University, Raleigh, NC, USA, \email{gremaud@ncsu.edu} \and J.L. Hart \at Department of Mathematics, North Carolina State University, Raleigh, NC, USA, \email{jlhart3@ncsu.edu}}
%}
\maketitle
\thispagestyle{empty}

%\newpage
%\textbf{BlueFern Supercomputing Unit, University of Canterbury, New Zealand}
\begin{abstract}
Cell models have increased in complexity with a concomitant increase in the associated number of parameters (notably the requirement that the models should possess complex cellular functions which are thought \textit{but not necessarily proven} to be important). These parameters, in defining the relevant phenomenon, more often than not come from a plethora of animal experiments whose relationship to the human physiology is weak with very little information on the errors in these measurements.  Sensitivity analysis of these models has been almost impossible due to the large dimension of the parameter vector. A three section methodology for global sensitivity is presented through , linear regression, polynomial chaos theory and the production of Sobol indices. The methodology is utilised with the analysis of a physiologically validated numerical model of  neurovascular coupling. This particular case has a large parameter dimension (of the order of 300). The sensitivity analysis investigates three quantities of interest (QoIs), that of the  average value of $K^+$ in the extracellular space, the average volumetric flow rate through the perfusing vessel and the minimum value of the actin/myosin complex in the smooth muscle cell. The global sensitivity analysis provides ranked parameter values in order of importance for the three QoIs, giving insight into areas of possible physiological dysfunction and areas of further investigation. 
\end{abstract}
%\listoftodos
%\tableofcontents
%\newpage

\input{introduction}

\input{model}
  
\input{methodology}

\input{results}

\input{discussion}

\input{conclusion}

\input{appendix}

%\bibliographystyle{KathisBibstyle} % no .sty!
\bibliographystyle{spbasic} 
\bibliography{library}

\end{document}